---
title: "Liars Dice"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r libraries ,include=FALSE}
## Be sure to run the ESPN Scrape before running this

library(flexdashboard)
library(htmlwidgets)
library(jsonlite)
library(gridExtra)
library(readr)
library(ggthemes)
library(scales)
library(zoo)
library(knitr)
library(kableExtra)
library(RColorBrewer)
library(shiny)
library(DT)
library(rsconnect)
library(httr)
library(tidyverse)
library(writexl)

options(dplyr.summarise.inform=F)

```


```{r ,include=FALSE}
## Starting point - need to run the Liar's Dice Text Script first
data <- read_csv("text data.csv")

## Going to separate into two datasets
## One with the high level detail
## The other with the information at the game level
data <- data %>% 
  select(source ,game_num ,info)

game_summary <- data %>% 
  filter(str_detect(info ,pattern = "Result")) %>% 
  mutate(winner         = str_sub(info 
                                  ,start = str_locate(info ,"Result ")[,"end"]+1
                                  ,end   = str_locate(info ," wins ")[,"start"]-1
                                  )
         ,num_of_rounds = str_sub(info 
                                  ,start = str_locate(info ,"in ")[,"end"]+1
                                  ,end   = str_locate(info ," rounds")[,"start"]-1
                                  )
         )


round_detail <- data[which(as.numeric(str_detect(data$info ,pattern = "Result")) %in% 1) + 1,] %>% 
  mutate(detail = str_split(info ,pattern = ", ")) %>% 
  unnest(detail) %>% 
  mutate(player      = coalesce(str_sub(detail 
                                        ,start = 1
                                        ,end   = str_locate(detail ," - ")[,"start"]-1
                                        )
                                ,str_sub(detail 
                                        ,start = 1
                                        ,end   = str_locate(detail ," accuses ")[,"start"]-1
                                        )
                                )
         ,bid        = str_sub(detail 
                               ,start = str_locate(detail ," - ")[,"end"]+1
                               ,end   = -1
                               )
         ,die        = str_sub(bid 
                               ,start = 1
                               ,end   = str_locate(bid ," x ")[,"start"]-1
                               )
         ,number     = str_sub(bid 
                               ,start = str_locate(bid ," x ")[,"end"]+1
                               ,end   = -1
                               )
         ,accusation = as.numeric(detail == "liar") %>% lag()
         ,accused    = str_sub(detail
                               ,start = str_locate(detail ," accuses ")[,"end"]+1
                               ,end   = str_locate(detail ," \\( ")[,"start"]-1
                               )
         ,actual_num = str_sub(detail
                               ,start = str_locate(detail ," were | was ")[,"end"]+1
                               ,end   = -1
                               )
         ) %>% # write_xlsx("C:/Users/riese/Desktop/Liars Dice/liars_test.xlsx")
  filter(detail != "liar") %>% 
  group_by(game_num) %>% 
  mutate(next_player    = ifelse(accusation == 1, NA ,lead(player))
         ,row_num       = row_number()
         ,temp_num      = ifelse((coalesce(lag(accusation),0)==1|row_num==1) ,1 ,0)
         ,round_num     = cumsum(temp_num)
         ,turn_num      = accumulate(temp_num ,~if(.y==0) .x+1 else .y)
         ,lie_ind       = ifelse(lag(number) > actual_num ,"Y" ,"N")
         ,exact_bid_ind = ifelse(lag(number) == actual_num ,"Y" ,"N")
         ,round_loser   = ifelse(lie_ind == "Y" ,accused ,player)
         ) %>% 
  ungroup() %>% 
  select(source ,game_num ,round_num ,turn_num ,everything() ,-row_num ,-temp_num)

round_loser <- round_detail %>% 
  filter(is.na(bid)) %>% 
  select(game_num ,round_num ,round_loser)

dice_count_by_round_and_player <- round_detail %>% 
  select(game_num ,round_num ,player) %>% 
  distinct() %>% 
  left_join(round_loser ,by = c("game_num" ,"round_num")) %>%
  arrange(game_num ,player ,round_num) %>% 
  group_by(game_num ,player) %>% 
  mutate(lost_round_ind                  = as.numeric(player==round_loser)
         ,dice_remaining_at_end_of_round = 5-cumsum(lost_round_ind)
         ) %>% 
  ungroup() %>% 
  select(-lost_round_ind ,-round_loser) %>% 
  arrange(game_num ,round_num ,player)

players_by_game <- round_detail %>% 
  select(game_num ,player) %>% 
  distinct()

player_count_by_game <- players_by_game %>% 
  group_by(game_num) %>% 
  summarise(player_count = n()) %>% 
  ungroup() %>% 
  mutate(player_count = str_c(player_count ," Player"))

eliminator_by_round <- round_detail %>% 
  mutate(eliminator = if_else(round_loser == accused ,player ,accused)) %>%
  filter(is.na(bid)) %>% 
  select(game_num ,round_num ,turn_num ,player ,accused ,exact_bid_ind ,round_loser ,eliminator) %>%
  rename(accuser = player)

round_eliminated_by_game <- dice_count_by_round_and_player %>%
  filter(dice_remaining_at_end_of_round == 0) %>% 
  group_by(game_num ,player) %>% 
  summarise(round_eliminated = min(round_num)) %>% 
  ungroup()

final_round_by_game <- dice_count_by_round_and_player %>% 
  group_by(game_num) %>% 
  mutate(max_round_num = max(round_num)) %>% 
  ungroup() %>% 
  filter(round_num == max_round_num)

BestPlayer <- game_summary %>% 
  group_by(winner) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n) ,winner) %>% 
  slice(1) %>% 
  select(winner) %>% 
  pull()

PlayerCounts <- unique(player_count_by_game$player_count)
PlayerList <- unique(players_by_game$player)

```

Summary
=======================================================================

Sidebar {data-width=200 .sidebar}
-----------------------------------------------------------------------

### Filters

```{r}


selectInput("PlayerCountInput"
            ,"Select player count:"
            ,choices = PlayerCounts
            ,selected = "3 Player"
            ,multiple = FALSE)

```


Column {data-width=450}
-----------------------------------------------------------------------

### Total Wins

```{r}

renderPlot({
  players_by_game %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    left_join(game_summary %>% select(game_num ,winner) ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInput) %>% 
    group_by(player) %>% 
    summarise(wins = sum(as.numeric(player == winner))) %>% 
    ggplot(aes(x = reorder(player ,wins) ,y = wins ,fill = wins)) +
      geom_col() +
      coord_flip() +
      scale_y_continuous(labels = comma_format(accuracy = 1) ,breaks = pretty_breaks()) +
      scale_fill_gradientn(colors = c("darkred", "tomato1","palegreen", "darkgreen")) +
      guides(fill ="none") +
      geom_hline(yintercept = reactive_games() / as.numeric(str_extract(input$PlayerCountInput ,pattern = "[0-9]{1,2}"))
                 ,linetype = "longdash") + 
      theme_fivethirtyeight()
})



```

### Total Dice Eliminated

```{r}

renderPlot({
  eliminator_by_round %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>%
    filter(player_count == input$PlayerCountInput) %>% 
    group_by(eliminator) %>% 
    summarise(dice_eliminated = n()) %>% 
    ungroup() %>% 
    ggplot(aes(x = reorder(eliminator ,dice_eliminated) ,y = dice_eliminated)) +
      geom_col() +
      coord_flip() +
      theme_fivethirtyeight()
})
  

```


Column {data-width=350}
-----------------------------------------------------------------------

### Games Played

```{r}

reactive_games <- reactive({
  game_summary %>%
    left_join(player_count_by_game ,by = c("game_num")) %>%
    filter(player_count == input$PlayerCountInput) %>% 
    summarise(n = n_distinct(game_num)) %>% 
    pull()
})

renderValueBox({
  valueBox(reactive_games()
           ,icon = "fa-dice"
           )
})

```

### Total Rounds Played

```{r}

renderPlot({
  players_by_game %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    left_join(game_summary %>% select(game_num ,winner ,num_of_rounds) ,by = c("game_num")) %>% 
    left_join(round_eliminated_by_game ,by = c("game_num" ,"player")) %>% 
    filter(player_count == input$PlayerCountInput) %>% 
    mutate(total_potential_rounds = as.numeric(str_extract(player_count ,pattern = "[0-9]{1,2}")) * 5
           ,rounds_potential      = coalesce(round_eliminated ,total_potential_rounds) %>% as.numeric()
           ,rounds_actual         = coalesce(round_eliminated ,as.numeric(num_of_rounds))) %>% 
    group_by(player) %>% 
    arrange(game_num) %>% 
    mutate(game_count = row_number()) %>% 
    arrange(player ,game_num) %>% 
    group_by(player) %>% 
    mutate(cum_rounds_potential = cumsum(rounds_potential)
           ,cum_rounds_actual   = cumsum(rounds_actual)
           ) %>% 
    ungroup() %>% 
    select(game_count ,player ,contains("cum_rounds")) %>% 
    pivot_longer(names_to = "type" ,values_to = "rounds" ,-c(game_count ,player)) %>% 
    mutate(type2 = if_else(type == "cum_rounds_actual" ,"Actual" ,"Plus Remaining Dice")) %>% 
    group_by(player ,type2) %>% 
    summarise(rounds = max(rounds)) %>% 
    ungroup() %>% 
    ggplot(aes(x = reorder(player ,rounds) ,y = rounds)) +
      geom_col() +
      coord_flip() +
      facet_wrap(. ~ type2) +
      scale_y_continuous(labels = comma_format(accuracy = 1) ,breaks = pretty_breaks()) +
      theme_fivethirtyeight()
})

```

### Dice Remaining over Time

```{r}

renderPlot({
  players_by_game %>% 
    left_join(final_round_by_game %>% select(game_num ,player ,dice_remaining_at_end_of_round) 
              ,by = c("game_num" ,"player")) %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInput) %>% 
    mutate(dice_remaining_at_end_of_round = coalesce(dice_remaining_at_end_of_round ,0)) %>% 
    arrange(player ,game_num) %>% 
    group_by(player) %>% 
    mutate(cumulative_dice_remaining = cumsum(dice_remaining_at_end_of_round)
           ,game_count               = row_number()
           ) %>% 
    ungroup() %>%
    ggplot(aes(x = game_count ,y = cumulative_dice_remaining ,color = player)) +
      geom_line(size = 0.71) +
      scale_y_continuous(labels = comma_format(accuracy = 1) ,breaks = pretty_breaks()) +
      theme_fivethirtyeight()
})

```

Other Stats
=======================================================================

Sidebar {data-width=200 .sidebar}
-----------------------------------------------------------------------

### Filters

```{r}

selectInput("PlayerCountInputPage2"
            ,"Select player count:"
            ,choices = PlayerCounts
            ,selected = "3 Player"
            ,multiple = FALSE)

```

Column {data-width=450}
-----------------------------------------------------------------------

### Turns Played

```{r}

reactive_turns <- reactive({
  round_detail %>% 
    filter(is.na(bid)) %>% 
    select(game_num ,round_num ,turn_num) %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>%
    filter(player_count == input$PlayerCountInputPage2) %>% 
    summarise(total_turns = sum(turn_num)) %>% 
    pull() %>% 
    prettyNum(big.mark = ",")
})

renderValueBox({
  valueBox(reactive_turns()
           ,icon = "fa-clock"
           )
})

```

### Win Streak

```{r}

renderPlot({
  players_by_game %>% 
    left_join(game_summary %>% select(game_num ,winner) ,by = c("game_num")) %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInputPage2) %>% 
    mutate(win = as.numeric(player == winner)) %>% 
    arrange(player ,game_num) %>% 
    group_by(player) %>%
    summarise(LongestLoseStreak  = max(rle(win)$lengths[rle(win)$values==0])
              ,LongestWinStreak  = max(rle(win)$lengths[rle(win)$values==1])
              ,CurrentLoseStreak = ifelse(rle(win)$values[length(rle(win)$values)]==0 ,rle(win)$lengths[rle(win)$values==0][length(rle(win)$lengths[rle(win)$values==0])] ,0)
              ,CurrentWinStreak  = ifelse(rle(win)$values[length(rle(win)$values)]==1 ,rle(win)$lengths[rle(win)$values==1][length(rle(win)$lengths[rle(win)$values==1])] ,0)
                ) %>%
    ungroup() %>% 
    select(player ,contains("Win")) %>% 
    pivot_longer(names_to = "streak_type" ,values_to = "streak" ,-player) %>% 
    mutate(streak_type2 = factor(if_else(streak_type == "LongestWinStreak" ,"Longest" ,"Active")
                                 ,levels = c("Longest" ,"Active"))) %>%
    ggplot(aes(x = reorder(player ,streak) ,y = streak)) +
      geom_col() +
      coord_flip() +
      facet_wrap(. ~ streak_type2) +
      theme_fivethirtyeight()
})

```

### Lose Streak

```{r}

renderPlot({
  players_by_game %>% 
    left_join(game_summary %>% select(game_num ,winner) ,by = c("game_num")) %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInputPage2) %>% 
    mutate(win = as.numeric(player == winner)) %>% 
    arrange(player ,game_num) %>% 
    group_by(player) %>%
    summarise(LongestLoseStreak  = max(rle(win)$lengths[rle(win)$values==0])
              ,LongestwinStreak  = max(rle(win)$lengths[rle(win)$values==1])
              ,CurrentLoseStreak = ifelse(rle(win)$values[length(rle(win)$values)]==0 ,rle(win)$lengths[rle(win)$values==0][length(rle(win)$lengths[rle(win)$values==0])] ,0)
              ,CurrentwinStreak  = ifelse(rle(win)$values[length(rle(win)$values)]==1 ,rle(win)$lengths[rle(win)$values==1][length(rle(win)$lengths[rle(win)$values==1])] ,0)
                ) %>%
    ungroup() %>% 
    select(player ,contains("Lose")) %>% 
    pivot_longer(names_to = "streak_type" ,values_to = "streak" ,-player) %>% 
    mutate(streak_type2 = factor(if_else(streak_type == "LongestLoseStreak" ,"Longest" ,"Active")
                                 ,levels = c("Longest" ,"Active"))) %>% 
    ggplot(aes(x = reorder(player ,streak) ,y = streak)) +
      geom_col() +
      coord_flip() +
      facet_wrap(. ~ streak_type2) +
      theme_fivethirtyeight()
})

```


Column {data-width=350}
-----------------------------------------------------------------------

### Lies Called

```{r}

renderPlot({
eliminator_by_round %>% 
  left_join(player_count_by_game ,by = c("game_num")) %>% 
  select(game_num ,round_num ,accuser ,accused ,player_count) %>% 
  pivot_longer(names_to = "accusation_type" ,values_to = "player" ,c(accuser ,accused)) %>%
  filter(player_count == input$PlayerCountInputPage2) %>% 
  group_by(player ,accusation_type) %>% 
  summarise(accusations = n()) %>% 
  ungroup() %>% 
  mutate(accusation_type2 = factor(if_else(accusation_type == "accuser" ,"Lies Called" ,"Called Liar")
                                   ,levels = c("Lies Called" ,"Called Liar"))
         ) %>% 
  filter(accusation_type2 == "Lies Called") %>% 
  ggplot(aes(x = reorder(player ,accusations) ,y = accusations)) +
    geom_col() +
    coord_flip() +
    theme_fivethirtyeight()
}) 

```

### Called Liar

```{r}

renderPlot({
eliminator_by_round %>% 
  left_join(player_count_by_game ,by = c("game_num")) %>% 
  select(game_num ,round_num ,accuser ,accused ,player_count) %>% 
  pivot_longer(names_to = "accusation_type" ,values_to = "player" ,c(accuser ,accused)) %>%
  filter(player_count == input$PlayerCountInputPage2) %>% 
  group_by(player ,accusation_type) %>% 
  summarise(accusations = n()) %>% 
  ungroup() %>% 
  mutate(accusation_type2 = factor(if_else(accusation_type == "accuser" ,"Lies Called" ,"Called Liar")
                                   ,levels = c("Lies Called" ,"Called Liar"))
         ) %>% 
  filter(accusation_type2 == "Called Liar") %>% 
  ggplot(aes(x = reorder(player ,accusations) ,y = accusations)) +
    geom_col() +
    coord_flip() +
    theme_fivethirtyeight()
}) 

```


### Honesty Percent when Called Liar

```{r}

renderPlot({
  eliminator_by_round %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInputPage2) %>%
    select(game_num ,round_num ,accuser ,accused ,round_loser ,player_count) %>% 
    mutate(honest_bid_ind = if_else(accused == round_loser ,"N" ,"Y")) %>% 
    group_by(accused) %>% 
    summarise(honest_bids  = sum(as.numeric(honest_bid_ind == "Y"))
              ,honesty_pct = honest_bids / n()) %>% 
    ungroup() %>% 
    ggplot(aes(x = reorder(accused ,honesty_pct) ,y = honesty_pct)) +
      geom_col() +
      coord_flip() +
      scale_y_continuous(labels = percent ,limits = c(0 ,1)) +
      geom_hline(yintercept = 0.5 ,linetype = "longdash") +
      theme_fivethirtyeight()
}) 

```


Player Page
=======================================================================

Sidebar {data-width=200 .sidebar}
-----------------------------------------------------------------------

### Filters

```{r}

selectInput("PlayerInput"
            ,"Select player:"
            ,choices = PlayerList
            ,selected = BestPlayer
            ,multiple = FALSE)

selectInput("PlayerCountInputPage3"
            ,"Select player count:"
            ,choices = PlayerCounts
            ,selected = "3 Player"
            ,multiple = FALSE)

```

Column {data-width=450}
-----------------------------------------------------------------------

### Perfect Bids Made

```{r}

reactive_perfect_bids <- reactive({
  round_detail %>% 
    filter(is.na(bid)) %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInputPage3) %>%    
    select(game_num ,round_num ,player ,accused ,exact_bid_ind) %>% 
    group_by(accused) %>% 
    summarise(exact_bids = sum(as.numeric(exact_bid_ind == "Y"))) %>% 
    ungroup() %>% 
    filter(accused == input$PlayerInput) %>% 
    select(exact_bids) %>% 
    pull() %>% 
    prettyNum(big.mark = ",")
})

renderValueBox({
  valueBox(reactive_perfect_bids()
           ,icon = "fa-trophy"
           )
})

```

### Perfect Bids Against

```{r}

reactive_perfect_bids_against <- reactive({
  round_detail %>% 
    filter(is.na(bid)) %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInputPage3) %>%    
    select(game_num ,round_num ,player ,accused ,exact_bid_ind) %>% 
    group_by(player) %>% 
    summarise(exact_bids_against = sum(as.numeric(exact_bid_ind == "Y"))) %>% 
    ungroup() %>% 
    filter(player == input$PlayerInput) %>% 
    select(exact_bids_against) %>% 
    pull() %>% 
    prettyNum(big.mark = ",")
})

renderValueBox({
  valueBox(reactive_perfect_bids_against()
           ,icon = "fa-thumbs-down"
           )
})

```

### Accusations by Opponent & Method

```{r}

renderPlot({
  eliminator_by_round %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    select(game_num ,round_num ,accuser ,accused ,round_loser ,eliminator ,player_count) %>% 
    filter(player_count == input$PlayerCountInputPage3) %>% 
    pivot_longer(names_to = "accusation_type" ,values_to = "player" ,c(accuser ,accused)) %>%
    mutate(accusation_type2 = factor(if_else(accusation_type == "accuser" ,"Lies Called" ,"Called Liar")
                                     ,levels = c("Lies Called" ,"Called Liar"))
           ,opponent        = if_else(player == round_loser ,eliminator ,round_loser)
           ) %>%     
    group_by(player ,opponent ,accusation_type2) %>% 
    summarise(success_count = sum(as.numeric(player != round_loser))
              ,total        = n()
              ,success_rate = success_count / total
              ) %>% 
    ungroup() %>% 
    pivot_longer(names_to = "result" ,values_to = "count" ,c(success_count ,total)) %>% 
    mutate(result = str_replace_all(result ,pattern = "success_count" ,"successful")) %>% 
    filter(player == input$PlayerInput) %>%
    ggplot(aes(x = reorder(opponent ,count) ,y = count ,fill = result)) +
      geom_col(position = "dodge") +
      coord_flip() +
      scale_fill_manual(values = c("#4DAF4A" ,"#377EB8")) +
      # scale_fill_brewer(palette = "Set1") +
      facet_wrap(. ~ accusation_type2) +
      scale_y_continuous(labels = comma ,breaks = pretty_breaks()) +
      theme_fivethirtyeight()
})


```

Column {data-width=350}
-----------------------------------------------------------------------

### Win Percent

```{r}

reactive_win_pct <- reactive({
  players_by_game %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    left_join(game_summary %>% select(game_num ,winner) ,by = c("game_num")) %>% 
    filter(player_count == input$PlayerCountInputPage3) %>% 
    group_by(player) %>% 
    summarise(wins                = sum(as.numeric(player == winner))
              ,total_games_played = n_distinct(game_num)
              ,win_pct            = round((wins / total_games_played) ,3) * 100
              ) %>% 
    ungroup() %>% 
    filter(player == input$PlayerInput) %>% 
    select(win_pct) %>% 
    pull()
})

renderGauge({
  gauge(reactive_win_pct()
        ,min = 0 
        ,max = 100 
        ,symbol = '%'
        ,sectors = gaugeSectors(success = c(38 ,100) ,warning = c(25 ,37.9) ,danger = c(0 ,24.9)))
})
  
```

### Dice Bid Distribution

```{r}

renderPlot({
  round_detail %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>%
    filter(player_count == input$PlayerCountInputPage3) %>% 
    filter(player == input$PlayerInput) %>% 
    filter(!is.na(bid)) %>% 
    mutate(die = factor(die)) %>% 
    group_by(player ,die) %>% 
    summarise(n = n()) %>%
    ggplot(aes(x = die ,y = n)) +
      geom_col() +
      coord_flip() +
      scale_y_continuous(labels = comma_format(accuracy = 1) ,breaks = pretty_breaks()) +
      theme_fivethirtyeight()
})

```


### Success Rate by Opponent & Method

```{r}

renderPlot({
  eliminator_by_round %>% 
    left_join(player_count_by_game ,by = c("game_num")) %>% 
    select(game_num ,round_num ,accuser ,accused ,round_loser ,eliminator ,player_count) %>% 
    filter(player_count == input$PlayerCountInputPage3) %>% 
    pivot_longer(names_to = "accusation_type" ,values_to = "player" ,c(accuser ,accused)) %>%
    mutate(accusation_type2 = factor(if_else(accusation_type == "accuser" ,"Lies Called" ,"Called Liar")
                                     ,levels = c("Lies Called" ,"Called Liar"))
           ,opponent        = if_else(player == round_loser ,eliminator ,round_loser)
           ) %>%     
    group_by(player ,opponent ,accusation_type2) %>% 
    summarise(success_count = sum(as.numeric(player != round_loser))
              ,total        = n()
              ,success_rate = success_count / total
              ) %>% 
    ungroup() %>% 
    filter(player == input$PlayerInput) %>%
    ggplot(aes(x = reorder(opponent ,total) ,y = success_rate)) +
      geom_col() +
      coord_flip() +
      facet_wrap(. ~ accusation_type2) +
      geom_hline(yintercept = .5 ,linetype = "longdash") +
      scale_y_continuous(labels = percent ,limits = c(0 ,1)) +
      theme_fivethirtyeight()
})

```





